Hemodynamic responses of the anterior "parahippocampal place area" (PPA) to a Hollywood movie's audio-description

### 2020-12-15 paper/main.tex
Revise and correct preprocessing description

\todo[inline]{part regarding motion correction/co-registration might be
incorrect}

\todo[inline]{what is missing: As I see it, AD must have been downsampled to
2.5x2.5x2.5 mm and AV must have been upsampled from 3.0 to 2.5mm??}

% data sources
% https://github.com/psychoinformatics-de/studyforrest-data-aligned/tree/master/code
% https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms}
fMRI time series of those 15 participants in the studyforrest dataset that took
part in all three experiments were obtained from
\href{https://github.com/psychoinformatics-de/studyforrest-data-aligned}{GitHub}.
Data were already corrected for motion and aligned by non-linear warping to a
participant-specific BOLD template image \citep{sengupta2016extension}.
% exclusion of VP 10
Data of one participant were dropped to due to invalid distortion correction
during scanning of the AD stimulus.
% preprocessing intro
All further analysis steps of the current study were carried out using tools of
FSL v5.0.9 (\href{https://www.fmrib.ox.ac.uk/fsl}{FMRIB's Software Library};
\citep{smith2004fsl}) on a computer cluster running the Debian GNU/Linux
operating system. Software packages were obtained from repositories of
\href{http://neuro.debian.net}{NeuroDebian} \citep{halchenko2012open}.

% my preprocessing
Preprocessing was carried out using FEAT v6.00 (FMRI Expert Analysis Tool;
\citep{woolrich2001autocorr}) as part of FSL.
% temporal filtering
High-pass temporal filtering was applied to every stimulus segment using a
Gaussian-weighted least-squares straight line with a cutoff period of
\unit[150]{s} (sigma=\unit[75.0]{s}) to remove low-frequency confounds.
% brain extraction
The brain was extracted from surrounding tissues using BET \citep{smith2002bet}.
% spatial smoothing
Data were spatially smoothed applying a Gaussian kernel with full width at half
maximum (FWHM) of \unit[4.0]{mm}.
% normalization
A grand-mean intensity normalization of the entire 4D dataset was performed by a
single multiplicative factor.
% pre-whithening
Correction for local autocorrelation in the time series (prewhitening) was
applied using FILM (FMRIB's Improved Linear Model; \citep{woolrich2001autocorr})
to improve estimation efficiency.

>>>>

% data sources
% https://github.com/psychoinformatics-de/studyforrest-data-aligned/tree/master/code
% https://github.com/psychoinformatics-de/studyforrest-data-templatetransforms}
All analyses presented here are based on previously published fMRI data
(\url{https://github.com/psychoinformatics-de/studyforrest-data-aligned}).
Of those 15 participants in the studyforrest dataset that took
part in all three experiments,
% exclusion of VP 10
data of one participant were dropped to due to invalid distortion correction
during scanning of the AD stimulus.
Data were previously corrected for motion, aligned with and re-sliced onto a
participant-specific BOLD template image \citep{sengupta2016extension}
(uniform spatial resolution of \unit[2.5$\times$2.5$\times$2.5]{mm} for both
AD and AV data).
% preprocessing intro
All analyses presented here were carried out using
FSL v5.0.9 (\href{https://www.fmrib.ox.ac.uk/fsl}{FMRIB's Software Library};
\citep{smith2004fsl}) on a computer cluster running the Debian GNU/Linux
operating system. Software packages were obtained from repositories of
\href{http://neuro.debian.net}{NeuroDebian} \citep{halchenko2012open}.

% my preprocessing
Preprocessing was performed by FEAT v6.00 (FMRI Expert Analysis Tool;
\citep{woolrich2001autocorr}) as shipped with FSL.
% temporal filtering
High-pass temporal filtering was applied to every stimulus segment using a
Gaussian-weighted least-squares straight line with a cutoff period of
\unit[150]{s} (sigma=\unit[75.0]{s}) to remove low-frequency confounds.
% brain extraction
The brain was extracted from surrounding tissues using BET \citep{smith2002bet}.
% spatial smoothing
Data were spatially smoothed applying a Gaussian kernel with full width at half
maximum (FWHM) of \unit[4.0]{mm}.
% normalization
A grand-mean intensity normalization of the entire 4D dataset was performed by a
single multiplicative factor.
% pre-whithening
Correction for local autocorrelation in the time series (prewhitening) was
applied using FILM (FMRIB's Improved Linear Model; \citep{woolrich2001autocorr})
to improve estimation efficiency.
